% -*-latex-*-
% $Log: cover.tex,v $
% Revision 1.8  2008/05/13 15:02:15  jdreed
% Degree month is June, not May.  Added note about prevdegrees.
% Arthur Smith's title updated
%
% Revision 1.7  2001/02/08 18:53:16  boojum
% changed some \newpages to \cleardoublepages
%
% Revision 1.6  1999/10/21 14:49:31  boojum
% changed comment referring to documentstyle
%
% Revision 1.5  1999/10/21 14:39:04  boojum
% *** empty log message ***
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.3  93/05/17  17:06:29  starflt
% Added acknowledgements section (suggested by tompalka)
% 
% Revision 1.2  92/04/22  13:13:13  epeisach
% Fixes for 1991 course 6 requirements
% Phrase "and to grant others the right to do so" has been added to 
% permission clause
% Second copy of abstract is not counted as separate pages so numbering works
% out
% 
% Revision 1.1  92/04/22  13:08:20  epeisach


% NOTE:
% These templates make an effort to conform to the MIT Thesis specifications,
% however the specifications can change.  We recommend that you verify the
% layout of your title page with your thesis advisor and/or the MIT 
% Libraries before printing your final copy.
\title{Improving Service Level Agreements for a Job Scheduler by Visualizing Simulations}


\author{Dina M. Betser}
% If you wish to list your previous degrees on the cover page, use the 
% previous degrees command:
%       \prevdegrees{A.A., Harvard University (1985)}
% You can use the \\ command to list multiple previous degrees
\prevdegrees{S.B., Massachusetts Institute of Technology (2011)}
\department{Department of Electrical Engineering and Computer Science}


% If the thesis is for two degrees simultaneously, list them both
% separated by \and like this:
% \degree{Doctor of Philosophy \and Master of Science}
\degree{Master of Engineering in Electrical Engineering and Computer Science}


% As of the 2007-08 academic year, valid degree months are September, 
% February, or June.  The default is June.
\degreemonth{June}
\degreeyear{2012}
\thesisdate{May 1, 2012}


%% By default, the thesis will be copyrighted to MIT.  If you need to copyright
%% the thesis to yourself, just specify the `vi' documentclass option.  If for
%% some reason you want to exactly specify the copyright notice text, you can
%% use the \copyrightnoticetext command.  
%\copyrightnoticetext{\copyright IBM, 1990.  Do not open till Xmas.}


% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{John Wilkes}{Google, Inc.}
\supervisor{Asuman Ozdaglar}{Associate Professor}


% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{Christopher J. Terman}{Chairman, Department Committee on Graduate Theses}


% Make the titlepage based on the above information.  If you need
% something special and can't use the standard form, you can specify
% the exact text of the titlepage yourself.  Put it in a titlepage
% environment and leave blank lines where you want vertical space.
% The spaces will be adjusted to fill the entire page.  The dotted
% lines for the signatures are made with the \signature command.
\maketitle


% The abstractpage environment sets up everything on the page except
% the text itself.  The title and other header material are put at the
% top of the page, and the supervisors are listed at the bottom.  A
% new page is begun both before and after.  Of course, an abstract may
% be more than one page itself.  If you need more control over the
% format of the page, you can use the abstract environment, which puts
% the word "Abstract" at the beginning and single spaces its text.


%% You can either \input (*not* \include) your abstract file, or you can put
%% the text of the abstract directly between the \begin{abstractpage} and
%% \end{abstractpage} commands.


% First copy: start a new page, and save the page number.
\cleardoublepage
% Uncomment the next line if you do NOT want a page number on your
% abstract and acknowledgments pages.
% \pagestyle{empty}
\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{abstract}
\end{abstractpage}


% Additional copy: start a new page, and reset the page number.  This way,
% the second copy of the abstract is not counted as separate pages.
% Uncomment the next 6 lines if you need two copies of the abstract
% page.
% \setcounter{page}{\thesavepage}
% \begin{abstractpage}
% \input{abstract}
% \end{abstractpage}


\cleardoublepage


\section*{Acknowledgments}


I am so grateful for the many people who made this thesis possible. My M.Eng. project has been the greatest academic challenge I faced up to this point in my life, and as such, it proved to be an extremely educational growing experience.  I really appreciate everybody who has touched my life up to this point and has enabled me achieve what I have, but there are a few people whose contributions deserve additional attention.


There are a lot of people who helped me during my time at Google. Dr. John Wilkes, my Google intern host on the Omega team, was incredibly giving in both his time and in creative ideas. I was very fortunate to have a thesis supervisor who was so nurturing and patient in helping me with so many aspects of this project. The other person whose assistance with this project has been invaluable was Malte Schwarzkopf, who was my go-to grad student for technical guidance. He has done everything from explaining the details of the simulator used in my project to helping me debug arcane source control issues. I am very grateful to Evan Adams, another engineer at Google, who taught me a lot about software engineering and helped prepare me for a career in software engineering by emphasising software skills. Others who made a significant impact during my time at Google include Surabhi Gupta, Gloria Guo, and Dr. Dimitris Nakos. I was privileged to work with the Roma team, where I gained valuable skills in data visualization and learned a lot about the infrastructure that manages Google's compute clusters. There have been many more amazing, brilliant people at Google who have been invaluable over the past three years than I can list here, but I appreciate their time and am looking forward to working with them again in the future.


Thanks go out to my MIT thesis advisor, Professor Asu Ozdaglar, for providing guidance on the MIT-end of the thesis process. Professor Paul Gray was and continues to be an outstanding Course 6 advisor, and I feel so lucky to have been able to benefit from his advice and tutelage over the past four years. Thank you to those involved with the 6A program, including Professor John Guttag and Anne Hunter.


Thank you to my friends, whose encouragement and advice kept me going throughout the process. Special thanks go out to Jenny Liu, who acquainted me with the MIT thesis process and assisted me in fine-tuning my final project presentation, and to Jesse Dunietz, who helped me in the initial phases of designing and executing my project.


A very special thank you goes out to my parents and grandparents for always being supportive and believing in me. Without my family, I'd hardly be where I am today. They always know just what I need and make sure I'm headed on the right track.




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% -*-latex-*-
